---
title: "p8105_hw5_mfc2162"
author: "Madeline Cannon"
date: "11/3/2019"
output: github_document
---

## Problem 1

#### Load data and introduce missing values

```{r}

library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

```


#### Function to fill missing values

```{r}

fill_missing = function(vector) {
  if (is.numeric(vector)) {
    v_mean = mean(vector, na.rm=TRUE)
    vector[is.na(vector)] = v_mean
  }
  if (is.character(vector)) {
    vector[is.na(vector)] = "virginica"
  }
  return(vector)
}

```


#### Apply to dataset using map

```{r}

iris_with_missing = map_df(iris_with_missing, fill_missing)
iris_with_missing

```


## Problem 2

#### Read in data for each subject

```{r}

files = list.files("./data")
study = data.frame()

get_data = function(file_name) {
  path = paste("./data/", file_name, sep = "")
  subject_data = read_csv(path)
  row = cbind(file_name, subject_data)
  study = rbind(study, row)
}

wide = map_dfr(files, get_data)

```


#### Tidy data

```{r}

study = wide %>%
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_",
               values_to = "observation") %>%
  mutate(id = substr(file_name, start = 5, stop = 6),
         arm = substr(file_name, start = 1, stop = 3),
         week = as.numeric(week)) %>%
  select(id, arm, week, observation)

study

```


#### Spaghetti plots

```{r}

control = study %>% filter(arm == "con")
experimental = study %>% filter(arm == "exp")

ggplot(data = control, aes(x = week, y = observation, color = id)) +
  geom_line() + xlab("Week") + ylab("Observation") + labs(color = "Subject ID") +
  ggtitle("Control")

ggplot(data = experimental, aes(x = week, y = observation, color = id)) +
  geom_line() + xlab("Week") + ylab("Observation") + labs(color = "Subject ID") +
  ggtitle("Experimental")

```

In the control group, the observations do not appear to change with time. In the experimental group, the observations clearly increase over time.


## Problem 3

#### Generate datasets

```{r}

set.seed(1)

sim_regression = function(n = 30, beta0 = 2, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0 ,50)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  results = ls_fit %>% broom::tidy() %>% filter(term == "x")
  
  tibble(
    b1_hat = coef(ls_fit)[2],
    p_value = pull(results, p.value)
  )
}


sim_results = 
  tibble(b1 = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = b1, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)

sim_results = sim_results %>% mutate(b1 = as.factor(b1))

```


#### Proportion of times the null was rejected

```{r}

sim_results = sim_results %>% mutate(reject_null = 0)

for (row in 1:nrow(sim_results)) {
  if (sim_results[row, "p_value"] < 0.05) {
    sim_results[row, "reject_null"] = 1
  }
}

power_plot = sim_results %>% group_by(b1) %>%
  summarize(proportion = sum(reject_null) / n())

ggplot(power_plot, aes(x=b1, y=proportion, fill=b1)) + geom_bar(stat="identity") +
  xlab("Beta 1") + ylab("Proportion") + theme(legend.position = "none")

```

As effect size increases, the power increases.


#### Average estimator of beta

```{r}

estimator_plot = sim_results %>% group_by(b1) %>%
  summarize(avg_est = mean(b1_hat))

ggplot(estimator_plot, aes(x=b1, y=avg_est, fill=b1)) + geom_bar(stat="identity") +
  xlab("True Beta 1") + ylab("Estimated Beta 1") + theme(legend.position = "none")

```